### 2015-06-26 narrative/intro.tex

>>>>

The Lightweight File Systems project from Sandia sought to strip down a file
system to the minimum features and encourage layering our auxiliary services to
add features for a particular use. Sirocco is the storage mechanism for LWFS.
We are proposing to combine the apps knowledge from ORNL with the SNL system
and the expertise gaps represented in the additional people to investigate how
to make a data, workflow, and application aware storage system.
